Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-15 hpmoon-asoco.tex
Addressing @JJ comments

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known
methods, suitable for dealing with large multi-objective optimization
problems. \textcolor{blue}{We propose a version of these algorithms where} each island modifies a fragment of the
chromosome that encodes a possible solution to the
problem. \textcolor{blue}{The objective of this paper is} to
demonstrate that automatically setting the size of the overlapping
fragments depending on the number of islands obtains better results
than using the same size. \textcolor{blue}{This method has been
  compared} to other parallel evolutionary techniques considering a
different number of islands, chromosome sizes and benchmarks. The
analysis of the obtained experimental results, by using different
metrics, shows that our approach can provide statistically significant
improvements with respect to the base algorithm in high-dimensional,
un-decomposable, multi-objective problems. This opens a very promising
line to automatically adapt the overlapping sizes in this kind of
algorithms.

@@

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
\begin{bluecolor}
One of the methods that are most extensively used  to deal with
high-dimensional, multi-objective optimization problems (MOPs) are
distributed co-evolutionary algorithms \cite{Gong15models}. However,
only decomposable problems could strictly be implemented in parallel
this way. A new parallel island-model evolutionary algorithm approach
\cite{Alba02Parallelism} is used here to deal with un-decomposable
problems: instead of sharing parts of individuals, each island, hosted
by a single processor, applies the variation operators to a specific
subset of the whole individual. This avoids extra steps (and
subsequent communication overhead) to recompose the complete
individuals from other islands before evaluation. 
\end{bluecolor}

@@

Different approaches have been used to parallelize EAs, as each individual can be considered as an
independent unit \citep{Alba13parallel,Gong15models}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
However, in the case of MOEAs, these
approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
 This implies \textcolor{blue}{using} different distribution
and sharing mechanisms, as there exists a tradeoff between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}. % Is that the case with NSGA? - JJ
% Please check the last question - JJ

@@

% Some introduction. ... We will describe here the design of the
% experiments bla bla bla--- JJ

This subsection describes the \textcolor{blue}{measurements of
  quality} used \textcolor{blue}{; these are}:

% Justify this - JJ
\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better. %Pablo: theoretical?
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@

% Move this to the top - JJ
Those metrics \textcolor{blue}{have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

>>>>

%%%NEW AND SHORTED
Parallel island-model co-evolutionary algorithms are well-known
methods, suitable for dealing with large multi-objective optimization
problems. \textcolor{blue}{This paper proposes a version of these algorithms where} each island modifies a fragment of the
chromosome that encodes a possible solution to the
problem. \textcolor{blue}{The objective of this paper is} to
demonstrate that automatically setting the size of the overlapping
fragments depending on the number of islands obtains better results
than using the same size. \textcolor{blue}{This method has been
  compared} to other parallel evolutionary techniques considering a
different number of islands, chromosome sizes and benchmarks. The
analysis of the obtained experimental results, by using different
metrics, shows that our approach can provide statistically significant
improvements with respect to the base algorithm in high-dimensional,
un-decomposable, multi-objective problems. This opens a very promising
line to automatically adapt the overlapping sizes in this kind of
algorithms.

@@

% Maybe add a sentence explaining what problems are decomposable and which ones are not. - JJ
% Pablo: ok, done in blue
\begin{bluecolor}
One of the methods that are most extensively used  to deal with
high-dimensional, multi-objective optimization problems (MOPs) are
distributed co-evolutionary algorithms \cite{Gong15models}. However,
only decomposable problems \textcolor{blue}{-that is, the ones whose  domain can be divided into subsets, calculate their solutions, and combine them to form the solution of the original problem-,} could strictly be implemented in parallel
this way. A new parallel island-model evolutionary algorithm approach
\cite{Alba02Parallelism} is used here to deal with un-decomposable
problems: \textcolor{blue}{instead of allocating disjoint subsets of components to the islands hosted by the available processors, it applies the variation operators only to the components  of the subset allocated to a given population, while keeping the rest of the components of the whole individual unaltered.}. This avoids extra steps (and
subsequent communication overhead) to recompose the complete
individuals from other islands before evaluation. 
\end{bluecolor}

@@

Different approaches have been used to parallelize EAs, as each individual can be considered as an
independent unit \citep{Alba13parallel,Gong15models}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
However, in the case of MOEAs, these
approaches \citep{Luna15Survey} need to deal with the whole solution set, the PF.
 This implies \textcolor{blue}{using} different distribution
and sharing mechanisms, as there exists a tradeoff between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}. \textcolor{blue}{This is also the case with the NSGA-II.} % Is that the case with NSGA? - JJ
% Please check the last question - JJ Pablo: done

@@

% Some introduction. ... We will describe here the design of the
% experiments bla bla bla--- JJ Pablo: Done
\textcolor{blue}{In this subsection, the design of the experiments will be described, starting with the measurements of quality, the benchmark problems, the different configurations compared, and the specific parameter set used.}

% Move this to the top - JJ Pablo: Done
\textcolor{blue}{Three different quality metrics have been used in this paper. These metrics have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better.
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@
